Verifying Demonstrations

### 2019-02-12 paper/intro.tex
Minor edits in intro

In this paper, our first main contribution is to propose \CROCUS, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.

Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against the original protocol of Brands and Chaum).
More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} and other types of resistance (see \cref{distance-bounding}), and provides a \ac{PK} for discrete logarithms.
The latter allows us to replace the use of the plain Schnorr protocol in the \ac{ZKPK} used in anonymous credentials,
%\seb{once again I think it is too strong to say that are the first to provide distance-bounding anonymous credentials as a a distance-bounding anonymous protocol can already be considered an anonymous credential in the sense that it allows to authenticate anonymously in addition of providing proximity testing
%and thus we are, to the best of our knowledge, the first to provide \ac{DB} anonymous credentials.}
%\sonja{Daniel, can you contrast that with the other DB AC approaches, what are they not general enough for, or what can we do they can't?}
and thus we are, to the best of our knowledge, the first to provide \emph{general} (\ie attribute-based, not only identity-based) \ac{DB} anonymous credentials.

>>>>

Our first contribution is \CROCUS, a privacy-preserving scheme that provides a 
way to securely estimate crowd counts in protests\footnote{%
  If location is ignored, it can be reduced to privacy-preserving yet 
  verifiable petitions.
}.

Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
Our adaptation fulfills all the requirements for modern \ac{DB} protocols, 
including \ac{DBDH} (which was an attack against the original protocol of 
Brands and Chaum) and \ac{DBTF}.
More importantly, it is public-key, handles malicious impersonating verifiers.
Since it is based on the Schnorr protocol, it provides a distance-bounded 
\ac{PK} for discrete logarithms.
That allows us to replace the plain Schnorr protocol in \acp{ZKPK} with our 
distance-bounding version and thus make general privacy-preserving, 
attribute-based credential systems distance bounding.
